\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-21 arch.tex
merged duplicate picture from kana with auv-agent

\begin{figure}[!htbp]
  \centering
  \includegraphics[scale=0.35]{figs/DAG-hierarchy}
  \caption{\small An example of a \rx reactor hierarchy which is used
    to determine a synchronization order for propagation of values in
    \emph{external} state variables.}
  \label{fig:reactor-DAG}
\end{figure}

As the execution frontier, $\tau$ advances, the \rx agent propagates
the current state information across all reactor state variables
through the {\em synchronization} process.  The sequencing of the
reactors synchronization is identified by traversing a reactor
dependency graph from the least dependent -- ones with no {\em
  external} timelines -- to the most, \ie which typically do not have
{\em internal} timelines. Fig. \ref{fig:reactor-DAG} shows an example
of such a dependency graph implemented as a directed acyclic graph.

>>>>

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[scale=0.35]{figs/DAG-hierarchy}
%   \caption{\small An example of a \rx reactor hierarchy which is used
%     to determine a synchronization order for propagation of values in
%     \emph{external} state variables.}
%   \label{fig:reactor-DAG}
% \end{figure}
\fcomment{I removed this figure as the next one is mucjh more
  detailed and vehiculate the same idea}

As the execution frontier, $\tau$ advances, the \rx agent propagates
the current state information across all reactor state variables
through the {\em synchronization} process.  The sequencing of the
reactors synchronization is identified by traversing a reactor
dependency graph from the least dependent -- ones with no {\em
  external} state variables -- to the most, \ie which typically do not have
{\em internal} state variables. Fig. \ref{fig:agent} shows an example
of such a dependency graph implemented as a directed acyclic graph.
